### 2014-03-12 src/analysis.Rnw
update

\begin{figure*}[t]
<<one.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
ggplot(subset(o.one, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of one element selection, All are above 0.98 $R^2$.}
\label{fig:onesel}
\end{figure*}

>>>>

\begin{figure*}[t]
<<one.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
ggplot(subset(o.one, values < 100 & (type=='line' | type=='method')), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of one element selection, All are above 0.98 $R^2$.}
\label{fig:onesel}
\end{figure*}
